Viscous Transport in Eroding Porous Media

### 2019-09-25 docs/transport/erosion_transport.tex
few changes that S-H found

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Governing Equations}
\label{sec:formulation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We start by defining the main variables used to model erosion.  We only
summarize the model, and a more detailed description is in our previous
work~\cite{qua-moo2018}.  We consider flows inside a confined geometry
$\Omega$ that contains $M$ eroding bodies with boundaries $\gamma_\ell$,
$\ell = 1,\ldots,M$.  The boundary of the bounding geometry is $\Gamma$,
so the boundary of the fluid domain is $\bd \Omega = \Gamma \cup
\gamma_1 \cup \cdots \cup \gamma_M$.  In all examples, we let $\Gamma$
be a slightly rounded-off version of $[-3,3] \times [-1,1]$, and we only
place eroding bodies in the region $[-1,1] \times [-1,1]$.  On each
eroding body, $\nn$ is the normal vector pointing into the body, and
$\ss$ is the unit tangent vector pointing in the counterclockwise
direction.  The normal vector on $\Gamma$ is the outward unit normal.
Neglecting inertial forces, the governing equations are
\begin{equation}
\label{eqn:erosionModel}
  \begin{split}
    \mu \Delta \uu = \grad p, &\hspace{20pt} \xx \in \Omega, \gap 
      &&\mbox{\em conservation of momentum}, \\
    \grad \cdot \uu = 0, &\hspace{20pt} \xx \in \Omega, \gap 
      &&\mbox{\em conservation of mass}, \\
    \uu = 0, &\hspace{20pt} \xx \in \gamma, \gap 
      &&\mbox{\em no slip on the bodies}, \\
    \uu = \UU, &\hspace{20pt} \xx \in \Gamma, \gap 
      &&\mbox{\em outer wall velocity}, \\
    \Vn = \CE \, \abs{\tau}, &\hspace{20pt} \xx \in \gamma,
      &&\mbox{\em erosion model}.
  \end{split}
\end{equation}
Here, $\uu$ is the fluid velocity, $p$ is the pressure, $\UU$ is a
prescribed Hagen-Poiseuille velocity field, $\Vn$ is the normal velocity
of $\gamma$, and
\begin{align}
  \tau = -(\nabla \uu + \nabla \uu^T) \nn \cdot \ss
  \label{eqn:shearStress}
\end{align}
is the shear stress on $\gamma$.  The strength of $\UU$ is adjusted at
each time step so that there is a constant pressure drop across the
channel.  We simulate erosion by alternating between solving the fluid
equations and adancing the grains according to the erosion rate for a
small time step.

@@

To rewrite the Stokes double-layer potential~\eqref{eqn:velocityDLP} in
terms of Cauchy integrals and their derivatives, we start by converting
it into a sequence of Laplace layer potentials~\cite{bar-wu-vee2015}
\begin{equation}
  \label{eqn:Stokes2Laplace}
  \begin{aligned}
    \DDD[\eeta](\xx) &= 
      \frac{1}{2\pi} \int_{\bd\Omega} 
        \frac{\nn}{\rho^2} (\rr \cdot \eeta) \, ds_\yy + 
      \frac{1}{2\pi} \nabla \int_{\bd\Omega}
        \frac{\rr \cdot \nn}{\rho^2} (\yy \cdot \eeta) \, ds_\yy \\
      &- \frac{1}{2\pi} x_1 \nabla \int_{\bd\Omega}
        \frac{\rr \cdot \nn}{\rho^2}\eta_1(\yy) \, ds_\yy -
      \frac{1}{2\pi} x_2 \nabla \int_{\bd\Omega}
        \frac{\rr \cdot \nn}{\rho^2}\eta_2(\yy) \, ds_\yy.
  \end{aligned}
\end{equation}
Therefore, the Stokes double-layer potential can be written in terms of
Cauchy integrals and their first derivative as
\begin{equation}
  \begin{aligned}
    u_1(x) &= \Re (v[\tau_1](x)) + \Re (v'[y\cdot\eta](x)) 
             -x_1\Re (v'[\eta_1](x)) - x_2\Re (v'[\eta_2](x)), \\
    u_2(x) &= \Re (v[\tau_2](x)) - \Im (v'[y\cdot\eta](x)) 
         +x_1\Im (v'[\eta_1](x)) + x_2\Im (v'[\eta_2](x)),
  \end{aligned}
  \label{eqn:cauchyVelocity}
\end{equation}
where $y \cdot \eta = y_1 \eta_1 + i y_2 \eta_2 \in \CC$, 
\begin{align} 
  \tau_1=(\eta_1+i\eta_2)\frac{\Re(n)}{n}, \quad
  \tau_2=(\eta_1+i\eta_2)\frac{\Im(n)}{n},
\end{align}
and $n \in \CC$ is the complex representation of the outward unit normal
$\nn \in \RR^2$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cauchy Integral Representation for the Gradient of the
Double-Layer Potential}
\label{sec:gradDLPcomplex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In addition to the velocity, we require a complex-valued layer potential representation
of the gradient of the velocity so that we can compute the shear stress
and the vorticity.  The deformation tensor at $x \in \Omega$ is found by
computing the derivatives of $u_1$ and $u_2$ as defined in
equation~\eqref{eqn:cauchyVelocity}  
\begin{equation}
\label{eqn:cauchyGradient}
  \begin{aligned}
    \pderiv{u_1}{x_1} &= +\Re (v'[\tau_1](x)) + 
      \Re (v''[y\cdot\eta](x)) - \Re (v'[\eta_1](x)) - 
      x_1\Re (v''[\eta_1](x)) - x_2\Re (v''[\eta_2](x)), \\
    \pderiv{u_1}{x_2} &= - \Im (v'[\tau_1](x)) - 
      \Im (v''[y\cdot\eta](x)) + x_1\Im (v''[\eta_1](x)) - 
      \Re (v'[\eta_2](x)) + x_2\Im (v''[\eta_2](x)), \\
    \pderiv{u_2}{x_1} &= +\Re (v'[\tau_2](x)) - 
      \Im (v''[y\cdot\eta](x)) + \Im (v'[\eta_1](x)) +
      x_1\Im (v''[\eta_1](x)) + x_2\Im (v''[\eta_2](x)), \\
    \pderiv{u_2}{x_2} &= -\Im (v'[\tau_2](x)) - 
      \Re (v''[y\cdot\eta](x)) + x_1\Re (v''[\eta_1](x)) +
      \Im (v'[\eta_2](x)) + x_2\Re (v''[\eta_2](x)).
  \end{aligned}
\end{equation}
The same expressions are used to compute the deformation tensor for $x
\in \bd\Omega$, except that the jump
condition~\eqref{eqn:deformationJump} is included.  Finally, to compute
the shear stress, the deformation tensor on $\bd\Omega$ is applied to
the normal and tangent vectors as defined in
equation~\eqref{eqn:shearStress}.  The gradient of the velocity field is
also used to compute the vorticity in the fluid bulk.  For $x \in
\Omega$, the Cauchy integral representation of the vorticity is
\begin{align}
  \omega(x) = \pderiv{u_2}{x_1} - \pderiv{u_1}{x_2} = 
\Re (v'[\tau_2](x)) + \Im (v'[\tau_1](x)) 
 + \Re (v'[\eta_2](x))+ \Im (v'[\eta_1](x)), \quad x \in \Omega.
\end{align}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Anomalous Dispersion}
\label{sec:dispersion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The dynamics of fluid in a porous media is often characterized in terms
of anomalous dispersion~\cite{kla-rad-sok2008, den-cor-sch-ber2004}.
The anomalous dispersion rate depends on the porosity and
permeability~\cite{koc-bra1988}, but is also affected by the
distribution and shape of the grains. We calculate the anomalous
dispersion rates by analyzing the streamlines governed by
equation~\eqref{eqn:tracers} in eroded geometries. Given a set of $N_p$
trajectories, we define $\lambda_j(t)$ to be the arclength of the
trajectory
\begin{align}
  \lambda_j(t) = \int_{0}^t \|\ss'_j(\tau)\|\, d\tau, 
    \quad j=1,\ldots,N_p.
\end{align}
Then, the first and second ensemble moments are
\begin{align}
  \label{eqn:moments}
  \langle \lambda \rangle (t) = 
    \frac{1}{N_p} \sum_{j=1}^{N_p} \lambda_j(t), \quad 
    \sigma_\lambda^2(t) = \frac{1}{N_p} 
    \left[\lambda_j(t) - \langle \lambda \rangle(t) \right]^2,
\end{align}
and $\sigma_\lambda$ characterizes particle dispersion.  At early times,
the particles have not explored much of the geometry, and we expect a
ballistic motion $\sigma_\lambda \sim t$.  However, as the particles
pass the grains, their trajectories are altered, and we expect that
$\sigma_\lambda \sim t^\alpha$, with $\alpha \in (0.5,1)$, indicating
that the flow is super-dispersive.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Tortuosity}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The tortuosity is a dimensionless number that quantifies the amount of
twisting of streamlines. Unlike the dispersion calculations, we do not
use reinsertion to form long trajectories.  The local tortuosity is
\begin{align}
  \tau(y_0) = \frac{\lambda(y_0)}{d}.
  \label{eqn:localTort}
\end{align}
Here, the streamline is initialized at the point $(x_0,y_0)$ on a
vertical cross-section of length $d$.  The hydraulic tortuosity is
defined by taking the average over all points on the cross-section
\begin{align}
  T = \frac{1}{d}\frac{\displaystyle\int_{S}u_1(x_0,y_0)\lambda(y_0)\,dy_0}
  {\displaystyle\int_{S}u_1(x_0,y_0)\,dy_0},
  \label{eqn:tortuosity1}
\end{align}
where $S$ is the cross-section $x = x_0$ that is perpendicular to the
$x$-axis with length $d$, and $u_1(y_0)$ is the $x$ component of the
velocity at the initial point of the streamline. Therefore, the
tortuosity satisfies $T \geq 1$, and $T=1$ only if no grains are
present.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Pore Throat Size}
\label{sec:throats}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
While transport in a porous media depends on the porosity, it also
depends on the placement of the grains.  In particular, the grain
placement affects velocity scales~\cite{ali-par-wei-bre2017},
correlation structures~\cite{leb-ded-dav-bou2007}, contaminant
transport~\cite{knu-car2005},
channelization~\cite{sie-ili-pri-riv-gua2019}, and more. In addition,
the grain configuration is important for pore network
models~\cite{bry-kin-mel1993, bry-mel-cad1993, bij-blu2006} that rely on
descriptions of the pore throat sizes. To characterize the grain
placement, we compute distributions of pore sizes between neighboring
grains.  To define neighboring grains, we form a Delaunay triangulation
using nodes placed at the center of each eroding grain and at a collection
of points around the boundary of the porous region.  Then, we say that
two grains are neighbors if their centers share an edge of the
triangulation~\cite{dea-qua-bir-jua2018}.  Finally, we compute the
minimum distance between all pairs of neighboring grains.  In
Figure~\ref{fig:Eroding100gap}(a), we plot a histogram of the pore size
of 100 eroded bodies.  The black curve is an unnormalized Weibull
distribution with the same mean and variance as the measured data.  In
Figure~\ref{fig:Eroding100gap}(b), we plot illustrate the pore throat
sizes by drawing the shortest lines between neighboring grains.  We do
not consider pores between eroding bodies and the solid and the
artificial points placed around the porous region, so some of the grains
near the porous region boundary only have two neighbors.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Governing Equations}
\label{sec:formulation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We start by defining the main variables used to model erosion.  We only
summarize the model, and a more detailed description is in our previous
work~\cite{qua-moo2018}.  We consider flows inside a confined geometry
$\Omega$ that contains $M$ eroding bodies with boundaries $\gamma_\ell$,
$\ell = 1,\ldots,M$.  The boundary of the bounding geometry is $\Gamma$,
so the boundary of the fluid domain is $\bd \Omega = \Gamma \cup
\gamma_1 \cup \cdots \cup \gamma_M$.  In all examples, we let $\Gamma$
be a slightly rounded-off version of $[-3,3] \times [-1,1]$, and we only
place eroding bodies in the region $[-1,1] \times [-1,1]$.  On each
eroding body, $\nn$ is the normal vector pointing into the body, and
$\ss$ is the unit tangent vector pointing in the counterclockwise
direction.  The normal vector on $\Gamma$ is the outward unit normal.
Neglecting inertial forces, the governing equations are
\begin{equation}
\label{eqn:erosionModel}
  \begin{split}
    \mu \Delta \uu = \grad p, &\hspace{20pt} \xx \in \Omega, \gap 
      &&\mbox{\em conservation of momentum}, \\
    \grad \cdot \uu = 0, &\hspace{20pt} \xx \in \Omega, \gap 
      &&\mbox{\em conservation of mass}, \\
    \uu = 0, &\hspace{20pt} \xx \in \gamma, \gap 
      &&\mbox{\em no slip on the bodies}, \\
    \uu = \UU, &\hspace{20pt} \xx \in \Gamma, \gap 
      &&\mbox{\em outer wall velocity}, \\
    \Vn = \CE \, \abs{\tau}, &\hspace{20pt} \xx \in \gamma,
      &&\mbox{\em erosion model}.
  \end{split}
\end{equation}
Here, $\uu$ is the fluid velocity, $p$ is the pressure, $\UU$ is a
prescribed Hagen-Poiseuille velocity field, $\Vn$ is the normal velocity
of $\gamma$, and
\begin{align}
  \tau = -(\nabla \uu + \nabla \uu^T) \nn \cdot \ss
  \label{eqn:shearStress}
\end{align}
is the shear stress on $\gamma$.  The strength of $\UU$ is adjusted at
each time step so that there is a constant pressure drop across the
channel.  We simulate erosion by alternating between solving the fluid
equations and advancing the grains according to the erosion rate for a
small time step.

@@

To rewrite the Stokes double-layer potential~\eqref{eqn:velocityDLP} in
terms of Cauchy integrals and their derivatives, we start by converting
it into a sequence of Laplace layer potentials~\cite{bar-wu-vee2015}
\begin{equation}
  \label{eqn:Stokes2Laplace}
  \begin{aligned}
    \DDD[\eeta](\xx) &= 
      \frac{1}{2\pi} \int_{\bd\Omega} 
        \frac{\nn}{\rho^2} (\rr \cdot \eeta) \, ds_\yy + 
      \frac{1}{2\pi} \nabla \int_{\bd\Omega}
        \frac{\rr \cdot \nn}{\rho^2} (\yy \cdot \eeta) \, ds_\yy \\
      &- \frac{1}{2\pi} x_1 \nabla \int_{\bd\Omega}
        \frac{\rr \cdot \nn}{\rho^2}\eta_1(\yy) \, ds_\yy -
      \frac{1}{2\pi} x_2 \nabla \int_{\bd\Omega}
        \frac{\rr \cdot \nn}{\rho^2}\eta_2(\yy) \, ds_\yy.
  \end{aligned}
\end{equation}
Therefore, the Stokes double-layer potential can be written in terms of
Cauchy integrals and their first derivative as
\begin{equation}
  \begin{aligned}
    u_1(x) &= \Re (v[\psi_1](x)) + \Re (v'[y\cdot\eta](x)) 
             -x_1\Re (v'[\eta_1](x)) - x_2\Re (v'[\eta_2](x)), \\
    u_2(x) &= \Re (v[\psi_2](x)) - \Im (v'[y\cdot\eta](x)) 
         +x_1\Im (v'[\eta_1](x)) + x_2\Im (v'[\eta_2](x)),
  \end{aligned}
  \label{eqn:cauchyVelocity}
\end{equation}
where $y \cdot \eta = y_1 \eta_1 + i y_2 \eta_2 \in \CC$, 
\begin{align} 
  \psi_1=(\eta_1+i\eta_2)\frac{\Re(n)}{n}, \quad
  \psi_2=(\eta_1+i\eta_2)\frac{\Im(n)}{n},
\end{align}
and $n \in \CC$ is the complex representation of the outward unit normal
$\nn \in \RR^2$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cauchy Integral Representation for the Gradient of the
Double-Layer Potential}
\label{sec:gradDLPcomplex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In addition to the velocity, we require a complex-valued layer potential representation
of the gradient of the velocity so that we can compute the shear stress
and the vorticity.  The deformation tensor at $x \in \Omega$ is found by
computing the derivatives of $u_1$ and $u_2$ as defined in
equation~\eqref{eqn:cauchyVelocity}  
\begin{equation}
\label{eqn:cauchyGradient}
  \begin{aligned}
    \pderiv{u_1}{x_1} &= +\Re (v'[\psi_1](x)) + 
      \Re (v''[y\cdot\eta](x)) - \Re (v'[\eta_1](x)) - 
      x_1\Re (v''[\eta_1](x)) - x_2\Re (v''[\eta_2](x)), \\
    \pderiv{u_1}{x_2} &= - \Im (v'[\psi_1](x)) - 
      \Im (v''[y\cdot\eta](x)) + x_1\Im (v''[\eta_1](x)) - 
      \Re (v'[\eta_2](x)) + x_2\Im (v''[\eta_2](x)), \\
    \pderiv{u_2}{x_1} &= +\Re (v'[\psi_2](x)) - 
      \Im (v''[y\cdot\eta](x)) + \Im (v'[\eta_1](x)) +
      x_1\Im (v''[\eta_1](x)) + x_2\Im (v''[\eta_2](x)), \\
    \pderiv{u_2}{x_2} &= -\Im (v'[\psi_2](x)) - 
      \Re (v''[y\cdot\eta](x)) + x_1\Re (v''[\eta_1](x)) +
      \Im (v'[\eta_2](x)) + x_2\Re (v''[\eta_2](x)).
  \end{aligned}
\end{equation}
The same expressions are used to compute the deformation tensor for $x
\in \bd\Omega$, except that the jump
condition~\eqref{eqn:deformationJump} is included.  Finally, to compute
the shear stress, the deformation tensor on $\bd\Omega$ is applied to
the normal and tangent vectors as defined in
equation~\eqref{eqn:shearStress}.  The gradient of the velocity field is
also used to compute the vorticity in the fluid bulk.  For $x \in
\Omega$, the Cauchy integral representation of the vorticity is
\begin{align}
  \omega(x) = \pderiv{u_2}{x_1} - \pderiv{u_1}{x_2} = 
\Re (v'[\psi_2](x)) + \Im (v'[\psi_1](x)) 
 + \Re (v'[\eta_2](x))+ \Im (v'[\eta_1](x)), \quad x \in \Omega.
\end{align}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Anomalous Dispersion}
\label{sec:dispersion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The dynamics of fluid in a porous media is often characterized in terms
of anomalous dispersion~\cite{kla-rad-sok2008, den-cor-sch-ber2004}.
The anomalous dispersion rate depends on the porosity and
permeability~\cite{koc-bra1988}, but is also affected by the
distribution and shape of the grains. We calculate the anomalous
dispersion rates by analyzing the streamlines governed by
equation~\eqref{eqn:tracers} in eroded geometries. Given a set of $N_p$
trajectories, we define $\lambda_j(t)$ to be the arclength of the
trajectory
\begin{align}
  \lambda_j(t) = \int_{0}^t \|\ss'_j(\tilde{t})\|\, d\tilde{t}, 
    \quad j=1,\ldots,N_p.
\end{align}
Then, the first and second ensemble moments are
\begin{align}
  \label{eqn:moments}
  \langle \lambda \rangle (t) = 
    \frac{1}{N_p} \sum_{j=1}^{N_p} \lambda_j(t), \quad 
    \sigma_\lambda^2(t) = \frac{1}{N_p} 
    \left[\lambda_j(t) - \langle \lambda \rangle(t) \right]^2,
\end{align}
and $\sigma_\lambda$ characterizes particle dispersion.  At early times,
the particles have not explored much of the geometry, and we expect a
ballistic motion $\sigma_\lambda \sim t$.  However, as the particles
pass the grains, their trajectories are altered, and we expect that
$\sigma_\lambda \sim t^\alpha$, with $\alpha \in (0.5,1)$, indicating
that the flow is super-dispersive.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Tortuosity}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The tortuosity is a dimensionless number that quantifies the amount of
twisting of streamlines. Unlike the dispersion calculations, we do not
use reinsertion to form long trajectories.  The local tortuosity is
\begin{align}
  \tau(y_0) = \frac{\lambda(y_0)}{d}.
  \label{eqn:localTort}
\end{align}
Here, the streamline originates at $(x_0,y_0)$ on the inlet and its
arclength is calculated once it passes the parallel outlet $x = x_0 +
d$.  The hydraulic tortuosity is defined by taking the average over all
points on the cross-section
\begin{align}
  T = \frac{1}{d}\frac{\displaystyle\int_{S}u_1(x_0,y_0)\lambda(y_0)\,dy_0}
  {\displaystyle\int_{S}u_1(x_0,y_0)\,dy_0},
  \label{eqn:tortuosity1}
\end{align}
where $S$ is the inlet cross-section $x = x_0$ that is perpendicular to
the $x$-axis, $u_1(y_0)$ is the $x$ component of the velocity at the
initial point of the streamline, and $d$ is still the distance between
the inlet and outlet. Therefore, the tortuosity satisfies $T \geq 1$,
and $T=1$ only if no grains are present.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Pore Throat Size}
\label{sec:throats}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
While transport in a porous media depends on the porosity, it also
depends on the placement of the grains.  In particular, the grain
placement affects velocity scales~\cite{ali-par-wei-bre2017},
correlation structures~\cite{leb-ded-dav-bou2007}, contaminant
transport~\cite{knu-car2005},
channelization~\cite{sie-ili-pri-riv-gua2019}, and more. In addition,
the grain configuration is important for pore network
models~\cite{bry-kin-mel1993, bry-mel-cad1993, bij-blu2006} that rely on
descriptions of the pore throat sizes. To characterize the grain
placement, we compute distributions of pore sizes between neighboring
grains.  To define neighboring grains, we form a Delaunay triangulation
using nodes placed at the center of each eroding grain and at a collection
of points around the boundary of the porous region.  Then, we say that
two grains are neighbors if their centers share an edge of the
triangulation~\cite{dea-qua-bir-jua2018}.  Finally, we compute the
minimum distance between all pairs of neighboring grains.  In
Figure~\ref{fig:Eroding100gap}(a), we plot a histogram of the pore size
of 100 eroded bodies.  The black curve is an unnormalized Weibull
distribution with the same mean and variance as the measured data.  In
Figure~\ref{fig:Eroding100gap}(b), we plot illustrate the pore throat
sizes by drawing the shortest lines between neighboring grains.  We do
not consider pores between eroding bodies and the solid wall $\Gamma$,
so some of the grains near the porous region boundary only have two
neighbors.
